Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-09 sports_analytics.Rmd
plural verb

In a similar Bayesian setting, @koopman2015dynamic studies English Premier League soccer match results by assuming a bivariate Poisson distribution with time-varying team abilities.
This state-space approach appears to improve on bookmaker's odds.

>>>>

In a similar Bayesian setting, @koopman2015dynamic study English Premier League soccer match results by assuming a bivariate Poisson distribution with time-varying team abilities.
This state-space approach appears to improve on bookmaker's odds.
